Observing Economic Growth in Unrecognized States with Nighttime Light \thanks{I thank Elizaveta Kugaevskaia for her superb research assistance on this project. Financial support from Japan Society for the Promotion of Science (JSPS Kakenhi Grant Number 17K13730) is gratefully acknowledged.}

### 2019-03-20 paper/paper.tex
Remove texts that were commented out in the background section #51

\subsection{Causes of Secession}
Ethnic conflicts are the underlying causes of secession in all the four cases of unrecognized states in the former Soviet Union.
%Ethnicity was salient in the Soviet Union: every citizen had to register their ethnicity at the age of 16 (de Waal 2013146).
During the lead-up to the collapse of the Soviet Union in 1991, Azerbaijan, Georgia, and Moldova all enacted nationalistic policies that put minority ethnic groups in a disadvantaged situation. 
These ethnic minorities no longer wanted to be part of the parent countries that declared independence from the Soviet Union.
Consequently, the wars of secession broke out.

@@

%\subsection{Nagorno-Karabakh}
%In 1923, the Soviet Union's authority drew the border of Nagorno-Karabakh Autonomous Oblast from scratch, based on their understanding of where Armenians resided within Azerbaijan.%
%\footnote{
%	An autonomous oblast is a district with some degree of autonomy from the government of a constituent republic of the Soviet Union. 
%} 
%The Soviet leaders made Nagorno-Karabakh part of Azerbaijan, rather than of Armenia, for two reasons, according to de Waal (2013:144--145). First, Moscow needed to appease Azeri politicians to control their oil fields in the Caspian Sea. Second, Armenians in Nagorno-Karabakh economically relied on the eastern part of Azerbaijan, and the communist ideal dictated that economic consideration should override ethnic integration.

%The 1994 ceasefire line was drawn based on the territory that Karabakh's army occupied by the end of the war. It significantly differs from the Soviet-era boundary of Nagorno-Karabakh as Karabakh Armenians have occupied the large chunk of land in the south-west corner of Azerbaijan to be geographically contiguous with Armenia.

\subsection{Economic Situations}\label{economic}
% Summarize King 2001:535-538
There is only sketchy information on economic situations in the four unrecognized states. King (2001:\ 535-538) reports one of the rare accounts, based on his own interviews with local residents in 2000.

@@

%Information is scant on economic conditions in Nagorno-Karabakh since the 1994 ceasefire. 
%International Crisis Group (2005:14--15) provides a rare account of Karabakh's economy as follows. 
%\begin{itemize}
%\item Entrepreneurs have been engaged in profitable scrap metal businesses by dismantling infrastructure, housing and other pre-war structures for the resale of metal, bricks and building materials in the occupied territory of Azerbaijan.
%\item Privatization of land and state enterprises has largely been completed. All residents outside the capital city of Stepanakert received 0.6 hectares of arable land. Private companies account for 80\% of the output. 
%\item Under-employment is widespread among rural residents although officials claim that the unemployment rate was 5.6\% in 2003. In 2005, the government started providing the unemployed with 60\% of the minimum wage.
%\item The government encourages child birth through various benefits for children: large families receive free electricity and books; couples with three children or more receive cash grants; and those with six children or more are given new homes.
%\item Income inequality is growing. In a survey of 1,000 by Stepanakert Press Club in October 2003, 40.5\% of the respondents answered that they lived better than five years ago while 57.6\% said their life got worse or didn't change.
%\end{itemize}

%On the other hand, Azerbaijan proper has experienced economic growth thanks to oil exports. 
%In 2006, the oil pipeline was opened from Baku, the capital city, to Turkey via Georgia, contributing to the world's fastest economic growth from 2005 to 2008 (de Waal 2013:291--292). 
%World Bank (2006:Table 1) reports that the percentage of people living in poverty fell from 44.6\% in 2002 to 24.0\% in 2005.
%This rapid decline is not concentrated in Baku and other urban areas but also seen in rural areas.

% \subsection{Abkhazia}
%International Alert (2004:123) reports that GDP per capita in Abkhazia was roughly estimated to be \$350 in 2001, dropped from \$1333 in 1988, with the population dependent on subsistence farming and humanitarian aid for survival.

 %\subsection{South Ossetia}
%Areshidze (2002), cited by International Crisis Group (2004:11), estimates that GDP per capita in South Ossetia was \$250 in 2002.

@@

\bibitem{} Mamuka Areshidze. 2002. ``Current Economic Causes of Conflict in Georgia.'' Unpublished report for UK Department for International Development (DFID).

@@

\bibitem{} Freedom House. 1998. ``Transnistria.'' \textit{Freedom in the World 1998}. \verb!freedomhouse.org/report/freedom-world/1998/transnistria! (accessed on 26 June, 2017). 

@@

\bibitem{} Freedom House 2015. ``South Ossetia.'' \textit{Freedom in the World 2012}. \verb!freedomhouse.org/report/freedom-world/2015/south-ossetia! (accessed on 15 March 2019).
\bibitem{} Freedom House 2016. ``South Ossetia.'' \textit{Freedom in the World 2012}. \verb!freedomhouse.org/report/freedom-world/2016/south-ossetia! (accessed on 15 March 2019).

@@

\bibitem{} International Alert. 2004. \textit{From War Economies to Peace Economies in the South Caucasus}. International Alert.

@@

\bibitem{} World Bank. 2006. ``Country Partnership Strategy FY07--10 for Republic of Azerbaijan.'' South Caucasus Country Management Unit, the World Bank.

>>>>

\subsection{Causes of Secession}
Ethnic conflicts are the underlying causes of secession in all the four cases of unrecognized states in the former Soviet Union.
During the lead-up to the collapse of the Soviet Union in 1991, Azerbaijan, Georgia, and Moldova all enacted nationalistic policies that put minority ethnic groups in a disadvantaged situation. 
These ethnic minorities no longer wanted to be part of the parent countries that declared independence from the Soviet Union.
Consequently, the wars of secession broke out.

@@

\subsection{Economic Situations}\label{economic}
There is only sketchy information on economic situations in the four unrecognized states. King (2001:\ 535-538) reports one of the rare accounts, based on his own interviews with local residents in 2000.

@@

@@

@@

@@

@@

@@
